Representing and Reasoning About Spatial Regions Defined by Context

### 2012-01-23 code/scenarios/cdsr/trunk/papers/AAAI2012/evaluation.tex
adding images

\subsection{Materials}
We evaluated our approach on six classrooms (two simulated and four real) and two simulated studio apartments. To determine how people define CDRSs, we asked \textbf{SOMENUMBER} of users to draw polygons for particular region types for each room. Users were also shown a polygon drawn by another user and asked to determine if it was an acceptable depiction of the region. All users provided acceptable regions, and therefore, we define the \textit{target region} as the union of the user-defined polygons.

\from{Nick}{What is the base CDSR in a problem instance?}

We consider a \textit{problem instance} to be a room and a sought CDSR type (e.g., ``front''). For each room for which we have a human-labelled target CDSR of the sought type, we generate an \textit{inferred region} using our analogical approach. To assess the quality of the transfer, we use the following measures:

>>>>

\subsection{Materials}

\from{Nick}{TODO: Perhaps list manually encoded CDSRs}

We evaluated our approach on six classrooms (two simulated and four real) and two simulated studio apartments. The simulated rooms were based on real-life counterparts. For each room we manually encoded the appropriate CDSRs that could be represented by our approach. These were used as the base CDSRs for analogical transfers, and can be considered the training data for our evaluation.

To determine how non-experts define CDRSs, we asked \textbf{SOMENUMBER} of users to draw polygons for particular region types for each room. Users were also shown a polygon drawn by another user and asked to determine if it was an acceptable depiction of the region. All users provided acceptable regions, and therefore, we define the \textit{target region} as the union of the user-defined polygons. The user-provided data provides the ground truth against which we evaluate our transfers.

We consider a \textit{problem instance} to be a room and a sought CDSR type. For each room for which we have a human-labelled target region of the sought type, we generate an \textit{inferred region} using analogical transfer. To assess the quality of the transfer, we calculate precision ($p$, the proportion of the inferred region that overlaps with the target region) and recall ($r$, the proportion of the target region that overlaps with the inferred region) as follows:
